Stats Project 2

### 2022-12-12 article.Rmd
added final ggplot to visualize model

```{r, echo=FALSE,fig.cap="Output Paramters of Model Summary", out.width= "60%",fig.align='center'}
knitr::include_graphics("./images/transform_paramters.png")
```

@@

From a complete analysis of the parameters in the model, we can create a proper assessment of the different regions and how the pricing changes per region in the data. From the parameters, what we've gathered is houses that are typically in the N. Ames region start at higher pricing, but scale their pricing slower with respect to sq. ft. compared to houses that are within the Brookside region. Although the Edwards housing region has marginally varying statistics to the Brookside region, they are not statistically significant enough to indicate any explain any variation by themselves, and thus housing prices should follow the same trend.

@@

```{r, echo=FALSE,fig.cap="Correlation Matrix"}
knitr::include_graphics("./images/numerical_correlation.png")
```

@@

```{r, echo=FALSE,fig.cap="Residuals for backwards elimination model"}
knitr::include_graphics("./images/residuals_backt1.png")
```

>>>>

```{r, echo=FALSE,fig.cap="Output Parameters of Model Summary", out.width= "60%",fig.align='center'}
knitr::include_graphics("./images/transform_paramters.png")
```

@@

From a complete analysis of the parameters in the model, we can create a proper assessment of the different regions and how the pricing changes per region in the data. From the parameters, what we've gathered is houses that are typically in the N. Ames region start at higher pricing, but scale their pricing slower with respect to sq. ft. compared to houses that are within the Brookside region. Although the Edwards housing region has marginally varying statistics to the Brookside region, they are not statistically significant enough to indicate any explain any variation by themselves, and thus housing prices should follow the same trend. We can visualize these by plotting the linear model of the data and visually confirm that the changes in slope and intercept are indeed represented in the model.

```{r, echo=FALSE,fig.cap="Plot of LR model", out.width= "40%",fig.align='center'}
knitr::include_graphics("./images/updatedlinearimage.png")
```

@@

```{r, echo=FALSE,fig.cap="Correlation Matrix", out.width="70%", fig.align='center'}
knitr::include_graphics("./images/numerical_correlation.png")
```

@@

```{r, echo=FALSE,fig.cap="Residuals for backwards elimination model", out.width= "60%", fig.align="center"}
knitr::include_graphics("./images/residuals_backt1.png")
```
